\documentclass[12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{alltt}
\usepackage{array}	
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{setspace}
\usepackage{listings}
\usepackage{amssymb,amsmath, amsthm}
\usepackage{qtree}
\usepackage{oz}
\usepackage[cc]{titlepic}
\usepackage{fancyvrb}


\title{SOEN331: Introduction to Formal Methods\\for Software Engineering\\
Assignment 2 on Object-Z specification}
\author{Julia Bazarbachian - 26781357\\
Rubiat Zaman - 40062082\\
Victor Manea - 40001995}
\date{March 4, 2019}

\begin{document}
\begin{spacing}{1.5}

\maketitle

\newpage

\section{Map}

{[Description, Coordinate]}
{\newline Point == Coordinate x Coordinate}
{\newline Message::= Success \textbar LocationAlreadyExists \textbar LocationUnknown}

\begin{class}{Map}
\also
\upharpoonright (AddLocation, DeleteLocation, ModifyLocation, FindLocation) \\
\begin{state}
locations: Description \leftrightarrow Point
\end{state} \\
\begin{init}
locations = \emptyset %\{ \}
\end{init} \\
\begin{op}{AddLocationOK}
\Delta (locations) \\
newDescription? : Description\\
point? : Point\\
\ST
newDescription? \notin dom~locations\\
locations' = locations \cup \{newDescription? \mapsto point? \}
\end{op}\\
\begin{op}{DeleteLocationOK}
\Delta (locations) \\
aDescription? : Description\\
\ST
aDescription? \in dom~locations\\
locations' = \{ aDescription? \} \ndres locations
\end{op}\\
\begin{op}{ModifyLocationOK}
\Delta (locations) \\
someDescription? : Description\\
somePoint? : Point
\ST
someDescription? \in dom~locations\\
locations' = locations \oplus \{ someDescription? \mapsto somePoint? \}
\end{op}\\
\begin{op}{FindLocationOK}
\Xi (locations) \\
description? : Description\\
getPoint! : Point
\ST
description? \in dom~locations\\
getPoint! = locations(description?)
\end{op}\\
\end{class}

\begin{class}{MapContinued}
\begin{op}{Successful}
result! : Message
\ST
result! = Success
\end{op}\\
\begin{op}{Repeated}
description? : Description\\
result! : Message
\ST
description? \in dom~locations\\
result! = LocationAlreadyExists
\end{op}\\
\begin{op}{Unknown}
description? : Description\\
result! : Message
\ST
description? \notin dom~locations\\
result! = LocationUnknown
\end{op}\\
\\
AddLocation \triangleq (AddLocationOK \wedge Successful) \vee Repeated\\
DeleteLocation \triangleq (DeleteLocationOK \wedge Successful) \vee Unknown\\
ModifyLocation \triangleq (ModifyLocationOK \wedge Successful) \vee Unknown\\
FindLocation \triangleq (FindLocationOK \wedge Successful) \vee Unknown\\
\end{class}

\begin{class}{Map2}
\also
\upharpoonright (AddLocation, DeleteLocation, ModifyLocation, FindLocation) \\
Map\\
\begin{state}
count : \mathbb {N}
\where
count >= 0
\end{state} \\
\begin{init}
count = 0
\end{init} \\
\begin{op}{AddLocationOK}
\Delta (count) \\
\ST
count' = count + 1
\end{op}\\
\begin{op}{DeleteLocationOK}
\Delta (count) \\
\ST
count > 0\\
count' = count - 1
\end{op}\\
\end{class}




\end{spacing}
\end{document}